### 2020-08-27 5_evaluation.tex
Update figure placement and performance numbers.

Figure~\ref{fig:bytes} shows performance with a memory-bound kernel. We measure a peak memory
bandwidth of 79~GB/s, using a working set size of 0.5 GB. As discussed in Section~\ref{sec:task-bench}, the kernels are designed to keep the working set constant as the number of iterations decrease to avoid noisy, superlinear effects in the results. For comparison, the
OpenMP-enabled STREAM benchmarks~\cite{STREAM} report up to 98~GB/s.

@@

We observe that overheads vary by over 5 orders of
magnitude. The most efficient systems are explicitly parallel
and provide very lightweight mechanisms for parallelism. Task-based systems for HPC tend to be next most efficient, and
provide additional features such as automatic dependency discovery and
data movement. Higher overhead systems tend to be designed primarily for
large-scale data analysis or workflows. It is worth
remembering that these are \emph{minimum}
effective task granularities. Applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

@@

%% From 1 to 3
%% dependencies, the ratio varies from $1.0\times$ to $150\times$ (median
%% $2.3\times$).

The ratio in METG between 0 and 3 dependencies per task ranges from
$1.01\times$ to $250\times$ (median $2.9\times$). The difference is most pronounced in systems that
perform runtime work inline. For example, MPI achieves an METG of 390
ns with 0 dependencies, but this rises to 4.6 \textmu{}s with 3 dependencies,
a $12\times$ increase. This is unsurprising, as with
0 dependencies no \lstinline[language=C++]{MPI_Isend} calls are
issued at all. Clearly, choosing a representative dependence
pattern is important when estimating the performance of a workload or
class of workloads.

@@

% Overall (out of 11 systems that perform well enough to have an intersection):
% Limit/Ideal vs Limit/Actual gap in nodes:
%   mean: 1.61x
%   median: 1.60x
%   min: 1.13x
%   max: 2.19x
% Limit/Ideal vs Limit/Actual gap in time:
%   mean: 1.28x
%   median: 1.27x
%   min: 1.01x
%   max: 1.69x

@@

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Section~\ref{subsec:scalability} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is at most $2.15\times$ in node count
and at most $1.42\times$ in time to solution, making this a
useful way to predict strong scaling in the 4 patterns we tested in
Section~\ref{subsec:scalability}.

>>>>

Figure~\ref{fig:bytes} shows performance with a memory-bound kernel. We measure a peak memory
bandwidth of 79~GB/s, using a working set size of 0.5 GB. As discussed in Section~\ref{sec:task-bench}, the kernels are designed to keep the working set constant as the number of iterations decrease to avoid noisy, superlinear effects in the results. For comparison, the
OpenMP-enabled STREAM benchmarks~\cite{STREAM} report up to 98~GB/s on the same hardware.

@@

We observe that overheads vary by over 5 orders of
magnitude. The most efficient systems are explicitly parallel
and provide very lightweight mechanisms for parallelism. Task-based systems for HPC tend to be next most efficient, and
provide additional features such as automatic dependency discovery and
data movement. Higher overhead systems tend to be designed primarily for
large-scale data analysis or workflows. It is worth
remembering that these are \emph{minimum}
effective task granularities. Applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

@@

The ratio in METG between 0 and 3 dependencies per task ranges from
$0.82\times$ to $250\times$ (mean $21\times$, std. dev. $64$). The
large standard deviation shows that the sensitivity of system overhead
to the dependency pattern varies widely. The largest ratios are among
systems that perform runtime work inline. For example, MPI achieves an
METG of 390 ns with 0 dependencies, but this rises to 4.6 \textmu{}s
with 3 dependencies, a $12\times$ increase. This is unsurprising, as
with 0 dependencies no \lstinline[language=C++]{MPI_Isend} calls are
issued at all. Clearly, choosing a representative dependence pattern
is important when estimating the performance of a workload or class of
workloads.

@@

@@

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Section~\ref{subsec:scalability} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is at most $1.96\times$ in node count
and at most $1.29\times$ in time to solution, making this a
useful way to predict strong scaling in the 4 patterns we tested in
Section~\ref{subsec:scalability}.
